Basics of Hardware Cache Optimization

### 2017-06-06 tex/methodology.tex
Tweak, fix typo

\begin{minted}[autogobble]{text}
   $ gcc -march=native -O2 program.c
   # cpupower frequency-set -g schedutil
   # chrt -f 99 ocount -e CPU_CLK_UNHALTED ./a.out
\end{minted}
%stopzone

>>>>

\begin{minted}[autogobble]{text}
   $ gcc -march=native -O2 program.c
   # cpupower frequency-set -g performance
   # chrt -f 99 ocount -e CPU_CLK_UNHALTED ./a.out
\end{minted}
%stopzone

### 2017-06-06 tex/motivation.tex
Revise, tweak, expand
Tweak, fix typo

% So what?  Why learn about hardware caches?  How much performance do I gain/lose
% depending on how cache-friendly my algorithm/code is?
\alts{Despite this, We will see that despite this}, two algorithms solving the same
problem with the same asymptotic complexity (in the same \(\Theta(g(n))\)) may differ in
performance by two orders of magnitude because of different \emph{memory access
patterns} (\cref{sec:map})~\cite{bigos}.  We will see an example of this in
\cref{sec:vvl}.

In a nutshell, hardware caches are ubiquitous but the performance improvements they
provide are conditional.
\begin{comment}
   To use them effectively,
   % To obtain optimal performance,
   algorithms must be designed and implemented with the architecture
   % design, structure, manner of functioning, inner workings, properties
   of hardware caches in mind.
\end{comment}
Effective use of hardware caches requires knowledge about \alts{how they work, their
architecture}.  Algorithms must be designed and implemented observing \alts{this
knowledge, their interactions with hardware caches}.

>>>>

% So what?  Why learn about hardware caches?  How much performance do I gain/lose
% depending on how cache-friendly my algorithm/code is?
\alts{Despite this, We will see that despite this}, two algorithms solving the same
problem with the same asymptotic complexity (in the same \(\Theta(g(n))\)) may differ in
performance by two orders of magnitude because of different \emph{memory access
patterns}\x{ (\cref{sec:map})}~\cite{bigos}.  We will see an example of this in
\cref{sec:vvl}.

In a nutshell, hardware caches are ubiquitous but the performance \alts{gains,
improvements} they provide are conditional.
\begin{comment}
   To use them effectively,
   % To obtain optimal performance,
   algorithms must be designed and implemented with the architecture
   % design, structure, manner of functioning, inner workings, properties
   of hardware caches in mind.
\end{comment}
Effective use of hardware caches requires knowledge about \alts{how they work, their
architecture}.  Algorithms must be designed and implemented observing \alts{this
knowledge, their interactions with hardware caches}.
